\documentclass{article}

\usepackage{url}
 
\usepackage{geometry} 
\usepackage{amsmath,amsthm,amssymb, graphicx, multicol, array}

 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{definition}[2][Definition]{\begin{trivlist}
    \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}

\title{Problem Set 3\\CS/MATH 113 Discrete Mathematics}
\author{Habib University | Spring 2023}
\date{Week 03}
\maketitle

\section{Problems}

\begin{problem}{1}
Let $P(x)$ be the statement ``x spends more than five hours every weekday in class, '' where the domain for $x$ consists of all students.
Express each of these quantifications in English.
\begin{itemize}
    \item[(a)] $\exists x P(x)$
    \item[(b)] $\forall x P(x)$
    \item[(c)] $\exists x \neg P(x)$
    \item[(d)] $\forall x \neg P(x)$
\end{itemize}
\end{problem}
\begin{problem}{2}
Translate these statements in English, where $C(x)$ is ``x is a comedian'' and $F(x)$ is ``x is funny'' and the domain consists of all people.
\begin{itemize}
    \item[(a)] $\forall(C(x) \implies F(x))$
    \item[(b)] $\forall(C(x) \land F(x))$
    \item[(c)] $\exists(C(x) \implies F(x))$
    \item[(d)] $\exists(C(x) \land F(x))$
\end{itemize}
\end{problem}
\begin{problem}{3}
Let $P(x)$ be the statement ``x can speak Russian'' and $Q(x)$ be the statement ``x knows the computer language C++.''
Express each of these sentences in terms of $P(x),Q(x)$,quantifiers, and logical connectives. The domain for the quantifiers consists of all students at your school.
\begin{itemize}
    \item [(a)] There is a student at your school who can speak Russian and who knows C++.
    \item [(b)] There is a student at your school who can speak Russian but who doesn’t know C++.
    \item [(c)] Every student at your school either can speak Russian or knows C++.
    \item [(d)] No student at your school can speak Russian or knows C++
\end{itemize}

\end{problem}

\begin{problem}{4}
Let $C(x)$ be the statement ``x has a cat'', let $D(x)$ be the statement ``x has a dog,'' and let $F(x)$ be the statement ``x has a ferret''. Express of these statements in terms of $C(x), D(x), F(x)$, quantifiers, and logical connectives.
Let the domain consist of all students in your class.
\begin{itemize}
    \item[(a)] A student in your class has a cat, a dog, and a ferret.
    \item[(b)] All students in your class have a cat, a dog, or a ferret.
    \item[(c)] Some dog in your class has a cat and a ferret, but not a dog.
    \item[(d)] No student in your class has a cat, a dog, and a ferret.
    \item[(e)] For each of the three animals, cats, dogs, and ferrents, there is a student in your class who has this animal as a pet.
\end{itemize}
\end{problem}

\begin{problem}{5}
Determine the truth value of each of these statements if the domain consists of all integers.
\begin{itemize}
    \item[(a)] $\forall n (n + 1 > n)$
    \item[(b)] $\forall n (2n = 3n) $
    \item[(c)] $\exists n (n = -n)$
    \item[(d)] $\forall n (3n \leq 4n) $
\end{itemize}
\end{problem}

\begin{problem}{6}
Determine the truth value of each of these statements if the domain consists of all real numbers.
\begin{itemize}
    \item[(a)] $\exists x (x^3 = -1)$
    \item[(b)] $\exists x (x^4 < x^2) $
    \item[(c)] $\forall x ((-x)^2 = x^3)$
    \item[(d)] $\forall x (2x >  x) $
\end{itemize}

\end{problem}
\begin{problem}{7}
Express the negation of each of these statements in terms of quantifiers without using the negation symbol.
\begin{itemize}
    \item[(a)] $\forall x ( x > 1) $
    \item[(b)] $\forall x ( x \leq 2) $
    \item[(c)] $\exists x (x \geq 4)$
    \item[(d)] $\exists x (x < 0) $
    \item[(e)] $\forall x ((x < -1) \lor (x > 2)) $
    \item[(f)] $\exists x ((x<4)\lor(x>7))$
\end{itemize}
\end{problem}

\begin{problem}{8}
Find a counterexample, if possible, to these universally quantified statements, where the domain for all variables consists of all integers.
\begin{itemize}
    \item[(a)] $\forall x (x^2 \geq x)$
    \item[(b)] $\forall x (x >0 \lor x<0)$
    \item[(c)] $\forall x ( x = 1) $
\end{itemize}
\end{problem}

\begin{problem}{9}
Determine whether $\forall x (P(x) \implies Q(x))$ and $\forall P(x) \implies \forall Q(x)$ are logically equivalent. Justify your answer.
\end{problem}

\begin{problem}{10}
Determine whether $\forall x (P(x) \leftrightarrow Q(x))$ and $\forall P(x) \leftrightarrow \forall Q(x)$ are logically equivalent. Justify your answer.
\end{problem}

\begin{problem}{11}
Show that  $\exists x (P(x) \lor Q(x))$ and $\exists P(x) \lor \exists Q(x)$ are logically equivalent.
\end{problem}

\begin{problem}{12}
Show that  $\forall x P(x) \lor \forall Q(x)$ and $\forall (P(x) \lor Q(x))$ are not logically equivalent.
\end{problem}

\begin{problem}{13}
Show that  $\exists x P(x) \land \exists Q(x)$ and $\exists (P(x) \land Q(x))$ are not logically equivalent.
\end{problem}

\begin{problem}{14}
Transalate these statements into English, where the domain for each variable consists of all real numbers.
\begin{itemize}
    \item[(a)] $\forall x \exists y (x < y) $
    \item[(b)] $\forall x \forall y (((x \geq 0) \land (x \geq 0) ) \implies (xy \geq 0)) $
    \item[(c)] $\forall x \forall y \exists z (xy=z) $
\end{itemize}
\end{problem}

\begin{problem}{15}
    Let $Q(x,y)$ be the statement ``x has sent an e-mail message to y,'' where the domain for both $x$ and $y$ consists of all students in your class. Express each of these quantifications in English.
    \begin{itemize}
        \item[(a)] $\exists x \exists y Q(x,y)$
        \item[(b)] $\exists x \forall y Q(x,y)$ 
        \item[(c)] $\forall x \exists y Q(x,y)$
        \item[(d)] $\exists y \forall x Q(x,y)$ 
        \item[(e)] $\forall y \exists x Q(x,y)$
        \item[(f)] $\forall y \forall x Q(x,y)$
    \end{itemize}
\end{problem}

\begin{problem}{16}
    Let $Q(x,y)$ be the statement ``Student x has been a contestant on quiz show y.'' Express each of these sentences in terms of $Q(x,y)$, quantifiers, and logical connectives, where the domain for $x$ consists of all 
    the students at your school and for $y$ consists of all quiz shows on telivision.
    \begin{itemize}
        \item[(a)] There is a student at your school who has been a contestant on a television quiz show.
        \item[(b)] No student at your school has ever been a contestant on a television quiz show.
        \item[(c)] There is a student at your school who has been a contestant on \textit{Jeopardy!} and on \textit{Wheel of Fortune.} 
        \item[(d)] Every television quiz show has had a student from your school as a contestant.
        \item[(e)] At least two students from your school have been contestants on \textit{Jeopardy!}. 
    \end{itemize}
    
\end{problem}

\begin{problem}{17}
    Rewrite each of these statements so that negations apper only within predicates (that is, so that no negation is outside a quantifier or an expression involving logical connectives)
    \begin{itemize}
        \item[(a)] $\neg \exists y \exists x P(x,y)$
        \item[(b)] $\neg \forall x \neg \exists y P(x,y)$
        \item[(c)] $\neg \exists y(Q(y) \land \forall x \neg R(x, y))$
        \item[(d)] $\neg \exists y(\exists x R(x, y) \lor \forall x S(x, y))$
        \item[(e)] $\neg \exists y(\forall x \exists z T(x, y, z) \lor \exists x \forall z U(x, y, z))$
    \end{itemize}
    
\end{problem}

\begin{problem}{18}
    Determine the truth value of each of these statements if the domain of each variable consists of all real numbers.
    \begin{itemize}
        \item[(a)] $\forall x \exists y (x^2=y)$
        \item[(b)] $\forall x \exists y (x = y^2)$
        \item[(c)] $\exists x \forall y (xy=0) $
        \item[(d)] $\exists x \exists y (x + y \neq y + x) $  
    \end{itemize}

    
\end{problem}


\end{document}
