\documentclass{article}

\usepackage{url}
 
\usepackage{geometry} 
\usepackage[shortlabels]{enumitem}
\usepackage{amsmath,amsthm,amssymb, graphicx, multicol, array}

 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\olsi}[1]{\,\overline{\!{#1}}} % overline short italic

 
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{definition}[2][Definition]{\begin{trivlist}
    \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}

\title{Problem Set 6\\CS/MATH 113 Discrete Mathematics}
\author{Habib University | Spring 2023}
\date{Week 07}
\maketitle

\section{Problems}

\begin{problem}{1}[Chapter 2.3, Question 1]
Why is $f$ not a function from $\mathbb{R}$ to $\mathbb{R}$ if 
\begin{enumerate}[(a)]
    \item $ f(x) = \frac{1}{x}$
    \item $ f(x) = \sqrt{x}$
    \item $ f(x) = \pm  \sqrt{(x^2 + 1)}$
    
\end{enumerate}
\end{problem}

\begin{problem}{2}[Chapter 2.3, Question 12, 13]
Determine whether each of these functions from $\mathbb{Z}$ to $\mathbb{Z}$ is one to one. Determine which functions are onto ?
\begin{enumerate}[(a)]
    \item $f(n) = n - 1$
    \item $f(n) = n^2 + 1$
    \item $f(n) = n^3 $
    \item $f(n) = \lceil \frac{n}{2} \rceil $
\end{enumerate}
\end{problem}

\begin{problem}{3}[Chapter 2.3, Question 22]
Determine whether each of these functions is a bijection from $\mathbb{R}$ to $\mathbb{R}$.
    \begin{enumerate}[(a)]
        \item $f(x) = -3x + 4$
        \item $f(x) = -3x^2 + 7$
        \item $f(x) = \frac{(x+1)}{(x+2)} $
        \item $f(x) = x^5 + 1 $
\end{enumerate}
\end{problem}


\begin{problem}{5}[Chapter 2.3, Question 24]
Let $ f: \mathbb{R} \rightarrow \mathbb{R}$ and let $ f(x) > 0 $ for all $ x \in \mathbb{R}$. Show that $f(x)$ is strictly increasing if and only if the function $g(x) = \frac{1}{g(x)}$ is strictly decreasing. 
\end{problem}


\begin{problem}{6}[Chapter 2.3, Question 26]
\begin{enumerate}[(a)]
    \item Prove that a strictly increasing function from $\mathbb{R}$ to itself is one to one.
    \item Give an example of an increasing function from $\mathbb{R}$ to itself is not one to one.
\end{enumerate}
\end{problem}


\begin{problem}{7}[Chapter 2.3, Question 29]
Show that the function $f(x) = \lvert x \rvert$ from the set of real numbers to the set of nonnegative real numbers is not invertible, but if the domain
is restricted to the set of nonnegative real numbers, the resulting function is invertible.

\end{problem}
\begin{problem}{8}[Chapter 2.3, Question 33]
Suppose that $g$ is a function from A to B and $f$ is a function from B to C.
\begin{enumerate}[(a)]
    \item Show that if both $f$ and $g$ are one-to-one functions,
    then $f \circ g$ is also one-to-one.
    \item Show that if both $f$ and $g$ are onto functions, then $f \circ g$
    is also onto.
\end{enumerate}    
    
\end{problem}
\begin{problem}{9}[Chapter 2.3, Question 34]
Suppose that $g$ is a function from A to B and $f$ is a function from B to C. Prove each of these statements
    \begin{enumerate}[(a)]
        \item If $f \circ g$ is onto, then $f$ must also be onto.
        \item If $f \circ g$ is one-to-one, then $g$ must also be one-to-one.
        \item If $f \circ g$ is a bijection, then $g$ is onto if and only if $f$ is one to one. 
    \end{enumerate}    
        
\end{problem}
\begin{problem}{10}[Chapter 2.3, Question 74]
    Suppose that $f$ is a function from A to B, where A and B
    are finite sets with $ \lvert A \rvert =  \lvert B \rvert$. Show that $f$ is one-to-one if
    and only if it is onto.
\end{problem}



\end{document}